\LARGE \bf A Formal Description of Bitcoin's Script Language

### 2017-03-20 paper.tex
Some corrections in related work, added intro paragraph to results section

In this section, we use our grammar

@@

The Bitcoin wiki Script article contains an explanation of how each opcode works in plain English, and information about the standard script templates that main nodes of the network will accept. While it does provide an informal explanation for each opcode (which came in handy when writing the operational semantics), its descriptions are rather unrigourous. On a few occasions descriptions are vague and ambiguous. For example, the explanation of \texttt{OP\_LEFT} is that it takes an argument to index a string and throws away everything to the right of the index, but it does not specify whether that operation is right-inclusive. Furthermore, this description cannot be used as input in automated theorem proving software.

The C++ reference implementation, by necessity, completely specifies the semantics of the language. However, the implementation also specifies details that are irrelevant to the syntactic correctness or valid/invalid judgement of a Script program. For example, the reference implementation defines a series of error codes, one for each possible cause of early termination with invalid state. This level of detail is not needed, and only complexifies reasoning about the language in the way we did in the results section. Additionally, as is the case with the existing Bitcoin wiki resource, we cannot directly use the language's implementation as axioms and rules to be used in a theorem prover.

Our proposed grammar, in constrast, unambiguously describes the behavior of Script and can (hopefully eventually) serve as basis for further analytic work.

>>>>

In this section, we make use of our formal specification to reason about execution time bounds of Script programs and to explain how a flaw in a prior version of the language was fixed.

@@

The Bitcoin wiki Script article contains an explanation of how each opcode works in plain English, and information about the standard script templates that main nodes of the network will accept. While it does provide an informal explanation for each opcode (which came in handy when writing the operational semantics), its descriptions are rather unrigourous, and sometimes even ambiguous. For example, the explanation of \texttt{OP\_LEFT} is that it takes an argument to index a string and throws away everything to the right of the index, but it does not specify whether that operation is right-inclusive. Finally, this resource cannot be used as input in automated theorem proving software.

The C++ reference implementation, by necessity, completely specifies the semantics of the language. However, the implementation also specifies details that are irrelevant to the syntactic correctness or valid/invalid judgement of a Script program. For example, the reference implementation defines a series of error codes, one for each possible cause of early termination with invalid state. These errors all cause the program execution to halt in the same way, and mainly serve to communicate the cause of an early termination to the running environment. Taking these various error codes into account needlessly complexifies the type of analyses we presented in our results section. Additionally, as is the case with the existing Bitcoin wiki resource, we cannot directly use the language's implementation as axioms and rules to be used in a theorem prover.

Our proposed grammar, in constrast, unambiguously describes the behavior of Script, is easier to reason about the C++ code, and can (hopefully eventually) serve as basis for further analytic work.
